Manuscript

### 2025-06-03 manuscript.qmd
update author contributions; number supplements

---
title: "Manuscript"
date: today
date-modified: today
date-format: iso
author:
  - name: Markus Bühner
    corresponding: true
    equal-contributor: true
    email: buehner@lmu.de
    orcid: 0000-0002-0597-8708
    role: 
      - formal analysis
      - supervision
      - writing
    affiliations:
      - id: "lmu"
        name: LMU Munich
        department: Department of Psychology
        address: Leopoldstr. 13
        city: D-80802 Munich
        country: Germany
        postal-code: 80802
  - name: Kathryn Eichhorn
    equal-contributor: true
    orcid: ~
    role: 
      - conceptualization
      - investigation
      - resources
      - data curation
      - writing
    affiliations:
      - name: University of the Bundeswehr Munich
        department: Institute of Psychology
        city: Neubiberg
        country: Germany
  - name: Florian Pargent
    orcid: 0000-0002-2388-553X
    role:
      - formal analysis
      - software
      - validation
      - editing
    affiliations:
      - ref: lmu
  - name: Janika Saretzki
    orcid: ~
    role:
      - visualization
      - editing
    affiliations:
      - name: University of Graz
        department: Department of Psychology
        city: Graz
        country: Austria
      - name: Charlotte Fresenius University of Psychology
        city: Munich
        country: Germany
      - ref: lmu
  - name: Jonas Hauck
    orcid: ~
    role:
      - editing
    affiliations:
      - id: "regen"
        name: University of Regensburg
        department: Faculty of Psychology
        city: Regensburg
        country: Germany
  - name: Sven Hilbert
    orcid: ~
    role:
      - conceptualization
      - supervision
      - editing
    affiliations:
      - ref: regen

@@

```{r}
#| label: "table1"
```

@@

results$table2
```

@@

results$table3
```

@@

results$table4
```

@@

results_secondary$table5
```

```{r}
#| label: "table6"
```

>>>>

---
title: "Manuscript"
date: today
date-modified: today
date-format: iso
author:
  - name: Kathryn Eichhorn
    equal-contributor: true
    orcid: 0000-0003-3676-9420
    role: 
      - conceptualization
      - investigation
      - resources
      - data curation
      - writing
    affiliations:
      - name: University of the Bundeswehr Munich
        department: Institute of Psychology
        city: Neubiberg
        country: Germany
  - name: Markus Bühner
    corresponding: true
    equal-contributor: true
    email: buehner@lmu.de
    orcid: 0000-0002-0597-8708
    role: 
      - formal analysis
      - supervision
      - writing
    affiliations:
      - id: "lmu"
        name: LMU Munich
        department: Department of Psychology
        address: Leopoldstr. 13
        city: D-80802 Munich
        country: Germany
        postal-code: 80802
  - name: Florian Pargent
    orcid: 0000-0002-2388-553X
    role:
      - formal analysis
      - software
      - validation
      - editing
    affiliations:
      - ref: lmu
  - name: Janika Saretzki
    orcid: ~
    role:
      - editing
    affiliations:
      - name: University of Graz
        department: Department of Psychology
        city: Graz
        country: Austria
      - name: Charlotte Fresenius University of Psychology
        city: Munich
        country: Germany
      - ref: lmu
  - name: Larissa Sust
    orcid: 0000-0002-3389-1626
    role:
      - editing
    affiliations:
      - ref: lmu
  - name: Jonas Hauck
    orcid: ~
    role:
      - editing
    affiliations:
      - id: "regen"
        name: University of Regensburg
        department: Faculty of Psychology
        city: Regensburg
        country: Germany
  - name: Sven Hilbert
    orcid: ~
    role:
      - conceptualization
      - supervision
      - editing
    affiliations:
      - ref: regen

@@

```{r}
#| label: "tbl-1"
#| tbl-cap: Descriptive statistics of demographic variables for 6 and 2 response categories
#| ft.align: left
#| disable-apaquarto-processing: false

results$table1
```

@@

results$table2
```
::: {.content-visible when-format="html"}
*Note.* Add table note for html format here.
:::

@@

results$table3
```
::: {.content-visible when-format="html"}
*Note.* Add table note for html format here.
:::

@@

results$table4
```
::: {.content-visible when-format="html"}
*Note.* Add table note for html format here.
:::

@@

results_secondary$table5
```
::: {.content-visible when-format="html"}
*Note.* Add table note for html format here.
:::

```{r}
#| label: "table6"
```
::: {.content-visible when-format="html"}
*Note.* Add table note for html format here.
:::
